Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-14 docs/google-research-awards-latam/main.tex
adding vilas

    Contact at Google:~Martin Barbella (mbarbella@google.com)

@@

\section{Related Work}
% Differential testing with fuzzing can improve the quality of programs
% Yang et al. \cite{yang-2011-finding}

In Patra and Pradel \cite{patra2016learning} was described a new black-box fuzzer tool 
that uses generative and probabilistic models to generate the entries. To evaluate the fuzzer,
Patra and Pradel uses JavaScript and HTML documents to improve the javascript engines
in Firefox and Chrome

Hodovan and Kiss \cite{hodovan-fuzzinator} exposes the Fuzzinator\footnote{https://github.com/renatahodovan/fuzzinator}
a random testing framework that uses distincts fuzzers to generate and ran test cases one-by-one in different
program components. Fuzzinator was evaluated on JerryScript\footnote{http://jerryscript.net} 
engine

@@

The basic workflow described in Section~\ref{sec:design} is functional. This section shows preliminary
results obtained with our infrastructure providing some evidence that finding bugs in runtime engines is
promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
issue trackers of different engines in the period of a month. For
example, bug \# 6 was manifested by the JS code \CodeIn{var a =
  \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
  === 0)\}}\footnote{This is a Lithium-minimized~\cite{lithium}
  version of the fuzzed code.}. In the original version of this code, the \CodeIn{valueOf} function returned
the empty string, whose integer representation, according to the spec,
should be zero\Fix{igor, please look for the part of spec and add link}. The modified
code returns a string representation of an invalid hexadecimal
value\Fix{igor, how do we know this is invalid?}. As such, the engines
are not expected to evaluate that string at the assertion expression;
hence test execution is expected to fail. Chakra,
however, is able to parse the string as a number. It returns a null
object, which is then converted to zero, making the test to pass.
\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
\begin{wraptable}[20]{tr}[0pt]{0.5\textwidth}
  \vspace{-2ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    10, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        & \checkm &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
   \bottomrule     
  \end{tabular}
\end{wraptable}

So far, six of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that, with the exception of one case, all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any bug on SpiderMonkey and V8. Finally, it is
worth noting that six of the 13 JS files that manifested
discrepancies were \emph{not} produced with fuzzing (column
``Fuzz''). These are test files from suites of different engines. This
observation emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from six different open
source engines, including a total of \Fix{38.9K} test files.

@@

\begin{itemize}
\item Integrate different fuzzers, including AFL~\cite{afl},
  HonggFuzz~\cite{honggfuzz}, jsfunfuzz~\cite{jsfunfuzz}, and
  Grammarinator~\cite{grammarinator}.

>>>>

    Contact at Google:~Martin Barbella (mbarbella@google.com) and Vilas Jagannath (vilasshekharbj@gmail.com)

@@

% \section{Related Work}
% Differential testing with fuzzing can improve the quality of programs
% Yang et al. \cite{yang-2011-finding}

@@

The basic workflow described in Section~\ref{sec:design} is functional. This section shows preliminary
results obtained with our infrastructure providing some evidence that finding bugs in runtime engines is
promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
issue trackers of different engines in the period of a month. For
example, bug \# 6 was manifested by the JS code \CodeIn{var a =
  \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
  === 0)\}}. 
  The \CodeIn{valueOf} is an object property that returns the primitive value
  of the specific object\cite{valueof} and in the original version of this code,
  the \CodeIn{valueOf} function returns an empty string.
  The modified code returns a string representation of an embedded null terminator
  value. 
  The unary plus ``\CodeIn{+a}" is equivalent to \CodeIn{Object.ToNumber(a.valueOf())} 
  that converts a variable to a number, otherwise the return should be the 
  value NaN (Not a Number) \cite{unary-plus}.
  As such, the engines evaluate that unary plus as a NaN value 
  at the assertion expression; hence test execution is expected to fail. 
  Chakra, however, is able to parse the string as a number zero, making the test to pass.

\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
\begin{wraptable}[20]{tr}[0pt]{0.5\textwidth}
  \vspace{-2ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    24, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
    14 & 5/17 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} \\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} \\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} \\
    17 & 5/24 & \checkm & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}\\
   \bottomrule     
  \end{tabular}
\end{wraptable}

So far, eight of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that, with the exception of one case, all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any bug on SpiderMonkey and V8. Finally, it is
worth noting that six of the 13 JS files that manifested
discrepancies were \emph{not} produced with fuzzing (column
``Fuzz''). These are test files from suites of different engines. This
observation emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from six different open
source engines, including a total of \Fix{38.9K} test files.

@@

\begin{itemize}
\item Integrate different fuzzers, including AFL~\cite{afl},
  HonggFuzz~\cite{honggfuzz}, LibFuzzer~\cite{libfuzzer}, jsfunfuzz~\cite{jsfunfuzz}, and
  Grammarinator~\cite{grammarinator}.
